Ribosome accumulation during early phase resistance training

### 2020-09-22 manuscript.Rmd
discussion notes

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur J. Øfsteng^2,£^, Nicolai B. Jacobsen^1^, Krister B. Flobergseter^1^,  Bent R. Rønnestad^1^, Stian Ellefsen^1,3^
date: ""
header-includes:
  - \usepackage{wasysym}
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
editor_options: 
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

>>>>

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur J. Øfsteng^2,£^, Nicolai B. Jacobsen^1^,
  Krister B. Flobergseter^1^,  Bent R. Rønnestad^1^, Stian Ellefsen^1,3^
date: ''
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
header-includes: \usepackage{wasysym}
editor_options:
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->
